---
title: "Lab 9"
author: "Gan Wei Cai (269979)"
date: "7/1/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Question 1
### Copy the following website’s content to a text file.  Read the text into R, name it as covid19.
This code show at below is the rvest package required to run this program.  
We can install the rvest package with the code: install.packages('rvest').
This package can allow us to read the html from the website.  
```{r}
library(rvest)
```
We use the web scraping method to read the html from the website and get the 
content of the website.
```{r}
webpage <- read_html('https://www.theedgemarkets.com/article/covid19-malaysia-reports-2068-new-cases')
results <- webpage %>% html_nodes("p")%>% html_text()
content <- results[9:21]
```
The code show below is how to create a file which the file named Covid19.txt  
We also can write the content which we get from the website into the file we have 
created.
```{r}
fileConn<-file("Covid19.txt")
writeLines(c(content), fileConn, sep = "\n\n")
close(fileConn)
```
We can read our text file that have been created by using readLines() function.
```{r}
readLines('Covid19.txt')
```

## Question 2
###	How many lines are there in the text file?
Get the number of the line in the text.
```{r}
x<-length(readLines('Covid19.txt'))
print(paste("Number of lines in this text file is",x))
```

## Question 3
###	How many textual lines (non-blank) are there in the file? Show only the lines with text.
Get the number of textual line in the text.
```{r}
x<-length(grep(" ", readLines('Covid19.txt')))
print(paste("The number of textual line is this text file is",x))
```
Display the line in text with the textual line.
```{r}
grep(" ", readLines('Covid19.txt'),value = TRUE)
```

## Question 4
### Show only lines with the word "Malaysia". How many lines?

Display the line with the word "Malaysia" only.
```{r}
grep("Malaysia",readLines('Covid19.txt'),value = TRUE)
```
Get the number of the line which only with the word "Malaysia" in the text.
```{r}
x<-length(grep("Malaysia",readLines('Covid19.txt'),value = TRUE))
print(paste("The number of line with the word 'Malaysia' is",x))
```

## Question 5
### Show lines with digits. (Remove all punctuation and special characters)
Display the text after removing all the punctuation and special characters in the text.  
We can use gsub() function to remove and replace the punctuation and special characters in the text.  
We replace them with a space.
```{r}
gsub("[^A-Za-z0-9]", " ", grep("[[:digit:]]",readLines('Covid19.txt'),value = TRUE))
```

## Question 6
### Extract digits and add them together. Show the result of the addition
We can use the stringr package to get the sum for all the digit in the text.
Before we use the stringr package, we have to install the stringr package.
Once we have installed the stringr package, we have to get the library for stringr package.
```{r}
library(stringr)
digit<- grep("[[:digit:]]",readLines('Covid19.txt'),value = TRUE)
digit<- gsub(",", "", digit)
x<-sum(as.numeric(unlist(str_extract_all(digit,"\\d*\\.*\\d"))))
print(paste("The sum of the digit in this text file is",x))
```


**Reference from the link https://www.theedgemarkets.com/article/covid19-malaysia-reports-2068-new-cases**