---
title: "Lab 7"
author: "User"
date: "`r format(Sys.time(), '%d %b %Y %H:%M:%S')`"
output: slidy_presentation
footer: Created by Gan Wei Cai

params:
  Name:
    label: Name
    value: ' '
    input: text
  Weight:
    label: Weight
    value: ' '
    input: numeric
  Height:
    label: Height
    value: ' '
    input: numeric
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


## Description
This is Lab 7 assignment that use a rmarkdown document to calculate the BMI.  
The user have to enter his/her name, weight, and height. Body mass index (BMI) 
is a value derived from the mass (weight) and height of a person. The BMI is 
defined as the body mass divided by the square of the body height, and is 
universally expressed in units of kg/m2, resulting from mass in kilograms and 
height in metres.

## BMI Function
Create a function named BMI with two argument which is weight and height.
The function should return two values which is status and BMI value. 
Depending the BMI value, a person can be categorized as 
underweight (BMI < 18.5), normal (18.5 ≤ BMI <25), overweight (25 ≥ BMI < 30),
or obese (BMI ≥ 30).
```{r, echo = TRUE}
BMI<-function(weight,height){
  BMI_value <- round(weight/(height^2),1)
  
  if(BMI_value<18.5){
    status<-"underweight"
  }
  if(BMI_value>=18.5&&BMI_value<25){
    status<-"normal"
  }
  if(BMI_value>=25&&BMI_value<30){
    status<-"overweight"
  }
  if(BMI_value>=30){
    status<-"obese"
  }
  result <- list(BMI_value,status)
  return(result)
}

x<-BMI(params$Weight,params$Height)
```


## Output
After the BMI function calculate the BMI, it will print the result as below.
```{r}
print(paste(paste(params$Name,"'s weight is",sep = ""),x[[2]],"and BMI is",x[[1]]))
```

