---
title: "Lab 8"
author: "User"
date: "23/12/2020"
output: html_document
params:
  birthdate:
    label: Select Your Birth Date
    value: ''
    input: date
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Part 1
This function is to calculate the age which we get the input from the parameters.  
The age is calculate by using as.POSIXlt function to do the subtraction.
```{r}
birthDate <- function(birthdate){
  age <-as.POSIXlt(Sys.Date())$year - as.POSIXlt(birthdate)$year
  return(age)
}

```


This is the result that we can print out.
```{r}
print(paste("The Birth Date is:",params$birthdate))
print(paste("The Current Date is",Sys.Date()))
print(paste("The age is",birthDate(params$birthdate)))
```

# Part 2
## Question 1
### How many species are there in the iris data frame?Name the species

By getting the number of count for the species, we can use nlevels function.
```{r}
nlevels(iris$Species)
```

We also can get the name of the species by using the levels function
```{r}
levels(iris$Species)
```

## Question 2
### Use one of the apply function to calculate the mean of Sepal.Length for all the species.

By using tapply function, we can easily to calculate the mean for Sepal.Length for all the species.
```{r}
tapply(iris$Sepal.Length,iris$Species,mean)
```

## Question 3
### Use one of the apply function to calculate the sums of the variables Sepal.Length, Sepal.Width, Petal.Length and Petal.Width

We can use the apply function to get the sum for each column but we need to remove the species
because it is in character. We can use the method that show below to create a new matrix which only consists the column which in numeric
```{r}
z <-as.matrix(iris[,-5])
apply(z,2,sum)
```
